Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2023-11-08 sections/combinatorial_semantics.tex
Working draft of pushouts in EHyp

    An e-hypergraph $\mathcal{G}$ over a monoidal signature $\Sigma$ is a tuple \[(V_{\mathcal{G}},E_{\mathcal{G}},s,t,l,<_c,\#)\] where $(V_{\mathcal{G}},E_{\mathcal{G}},s,t)$ are the same as in~\ref{def:hypergraph}.
    The labelling $l$ is modified to include an extra value $\bot \;$ $l :E_{\mathcal{G}} \to \Sigma + 1$. With an abuse of notation, we will confuse $\mathcal{G}$ with $V_{\mathcal{G}} \cup E_{\mathcal{G}}$, when treating it as a set.

    $<_c \subset \mathcal{G} \times \mathcal{G}$ is a child relation imposing a partial order on $\mathcal{G}$.
    We require that for a given $x \in \mathcal{G}$ a set of all predecessors of $x\;$ $[x) = \{x' \in \mathcal{G} \;||\; x' <_c x\; \}$ is finite and consists of edges $e \in E_{\mathcal{G}}$ such that $l(e) = \bot$ only.
    Next, each $x$ has at most one immediate predecessor.
    \update{We will denote the fact that $e$ is an immediate predecessor of $v$ as $e <_c^{\mu} v$.}
    % , which essentially makes $<_{c}$ into a function that for any given $x$ returns its immediate predecessor.
    Such order was called a \textbf{well-founded arborescent} strict partial order in~\cite{orders_and_events}.
    Similarly, a set of all successors is $(x] = \{x' \in \mathcal{G} \; ||\; x < x'\}$ where $x'$ can be a node or an edge. 
    % An edge $e \in E_{\mathcal{G}}$ is unlabelled, i.e. $l(e) = \bot$ iff $(e] \not = \varnothing$.
    Finally, we require that $<_c$ respects connectivity, i.e. if $v \in s(e)$ then $e' < e$ iff $e' <_c v$.

    $\langle \mathcal{G}, <_c, \# \rangle$ is an event-structure where $\# \subset \mathcal{G} \times \mathcal{G}$ is an irreflexive symmetric relation called \textit{conflict} relation which satisfies the following
    \begin{enumerate}
        \item 
        \[
    \forall x_1, x_2, x_3 \in \mathcal{G} \text{, if } x_1 <_c x_2 \text{ and } x_1 \# x_3 \text{ then } x_2 \# x_3
    \] 
    if $x_1 <_c x_2$ we say that conflict $x_2 \# x_3$ is inherited from the conflict $x_1 \# x_3$. If the conflict is not inherited we say it is \textit{immediate} and denote it with $\#_{\mu}$
    \item $<_c$ and $\#$ are mutually exclusive
    \item $\#$ is defined \textit{only} for $x \in \mathcal{G}$ such that $[x) \not \eq \varnothing$
    \item $\#$ should respect connectivity
    \item \update{Complement of $\#$ should be transitive}
    \item for all distinct $x_1, x_2, x_3 \in V \cup E$ $x_1 \#_{\mu} x_2$ and $x_2 \#_{\mu} x_3$ implies $x_1 \#_{\mu} x_3$
    \item for all $x, x' \in \mathcal{G}$ $x \#_{\mu} x'$ implies $[x) = [x')$
        \end{enumerate}

@@

    % \item
    % $x_1 \#_{\mathcal{F}} x_2$ iff $\phi(x_1) \#_{\mathcal{G}} \phi(x_2)$, where $x_1, x_2 \in \mathcal{F}$
    \question{
        \item
    if $x_1 \#_{\mathcal{F}} x_2$ then $\phi(x_1) \#_{\mathcal{G}} \phi(x_2)$, where $x_1, x_2 \in \mathcal{F}$
    }
\end{enumerate}

\update{Let's denote the fact of $x_1$ being the immediate predecessor of $x_2$ by $x_1 <_{\mu} x_2$. Also, note that preserving the immediate predecessor implies preserving order. Homomorphism definition seems to be fine: by not requiring the \textit{only if} direction in bullet 2 we basically allow either of two things

\begin{itemize}
    \item $\phi(x_1) <_{\mu} \phi(x_2)$ and $x_1 <_{\mu} x_2$
    \item $\phi(x_1) <_{\mu} \phi(x_2)$ and $x_1$ is unrelated to $x_2$
\end{itemize}

We can not have $\phi(x_1) <_{\mu} \phi(x_2)$ and $x_1 < x_2$, i.e. the case where $x_1$ is not the immediate predecessor of $x_2$ because then it would mean that there exists at least $x_3$ such that $x_1 <_{\mu} x_3 <_{\mu} x_2$ and because $\phi$ should preserve them it would mean that $\phi(x_1) <_{\mu} \phi(x_3) <_{\mu} \phi(x_2)$ implying that $\phi(x_2)$ has two immediate predecessors: $\phi(x_1)$ and $\phi(x_3)$.
Of course, if $\phi$ does not identify $x_1$ and $x_3$.
The first bullet is fine because it means that $\phi$ reflects the immediate predecessor.
The second bullet leaves us with two options depicted above.

\begin{figure}
    \centering
\begin{subfigure}{0.4\linewidth}

\scalebox{0.5}{
\begin{tikzpicture}
	\begin{pgfonlayer}{nodelayer}
		\node [style=node, label={above:$x_1$}] (19) at (-3.5, -4.5) {};
		\node [style=node, label={above:$x_2$}] (20) at (-4.5, -6.5) {};
		\node [style=node, label={above:$x_3$}] (21) at (-2.5, -6.5) {};
		\node [style=node, label={above:$x_4$}] (22) at (-3.5, -8.5) {};
		\node [style=node, label={above:$x_5$}] (23) at (-1.5, -8.5) {};
		\node [style=node, label={right:$x_2$}] (24) at (4.5, -5.5) {};
		\node [style=node, label={above:$x_1$}] (25) at (4.5, -2.5) {};
		\node [style=node, label={below:$x_5$}] (26) at (4.5, -11.5) {};
		\node [style=none] (27) at (4.5, -7.5) {};
		\node [style=none] (28) at (4.5, -9.5) {};
		\node [style=none] (29) at (4.5, -8.5) {$\vdots$};
		\node [style=none] (30) at (0.5, -6.5) {};
		\node [style=none] (31) at (2.5, -6.5) {};
		\node [style=none] (32) at (1.5, -5.5) {$\phi$};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw (19) to (20);
		\draw (19) to (21);
		\draw (21) to (22);
		\draw (21) to (23);
		\draw (24) to (27.center);
		\draw (26) to (28.center);
		\draw (25) to (24);
		\draw [style=diredge] (30.center) to (31.center);
	\end{pgfonlayer}
\end{tikzpicture}

\caption{Case 1}
\end{subfigure}
\hfill
\begin{subfigure}{0.4\linewidth}

\scalebox{0.5}{
\begin{tikzpicture}
	\begin{pgfonlayer}{nodelayer}
		\node [style=node, label={above:$x_1$}] (19) at (-6.5, -4.5) {};
		\node [style=node, label={above:$x_2$}] (20) at (-7.5, -6.5) {};
		\node [style=node, label={above:$x_3$}] (21) at (-5.5, -6.5) {};
		\node [style=node, label={above:$x_4$}] (30) at (-3, -4.5) {};
		\node [style=node, label={above:$x_1$}] (31) at (2.5, -4.5) {};
		\node [style=node, label={above:$x_2$}] (32) at (1.5, -6.5) {};
		\node [style=node, label={above:$x_3$}] (33) at (2.75, -6.5) {};
		\node [style=node, label={above:$x_4$}] (34) at (4, -6.5) {};
		\node [style=none] (35) at (-1.5, -5.5) {};
		\node [style=none] (36) at (-0.5, -5.5) {};
		\node [style=none] (37) at (-1, -5) {$\phi$};
	\end{pgfonlayer}
	\begin{pgfonlayer}{edgelayer}
		\draw (19) to (20);
		\draw (19) to (21);
		\draw (31) to (32);
		\draw (31) to (33);
		\draw (31) to (34);
		\draw [style=diredge] (35.center) to (36.center);
	\end{pgfonlayer}
\end{tikzpicture}

\caption{Case 2}

\end{subfigure}
\end{figure}

\update{Case (a) above is impossible on two occasions: for the image of $x_5$ to be a successor of the image of $x_2$, $x_5$ itself should be hierarchical. Then, because $\phi$ should preserve the immediate predecessor, the image of $x_3$ should be the immediate predecessor of the image of $x_5$ and the image of $x_1$ should be the immediate predecessor of the image of $x_3$ and of the image of $x_2$. Since the image of $x_2$ is a successor of the image of $x_5$ on the right there should be two paths from the image of $x_5$ to the image of $x_1$ one through the image of $x_3$ and another through the image of $x_2$, this effectively means that some node on this path has two immediate predecessors.

The case (b) above typechecks (for typed e-hypergraphs) only if $x_4$ is of type $0 \to 0$. This case is fine because we always can append, e.g. an edge, to a hierarchical edge using the semilattice equations (the one for tensoring the box). This also assumes that the image is down-closed.
}

\question{There is an issue with requiring that $\phi$ should reflect the conflict though. When we consider e-cospans and the maps from the interfaces to the carrier we map some nodes from the interface to conflicted nodes in the carrier. However, these nodes in the interface can not be in conflict as they have no predecessors. We can ask that this is a property of a matching morphism $m$ rather than arbitrary homomorphism. The same was done for down-closed-ness, for example.
}

@@

    We will compute pushouts in $\catname{EHyp_{\Sigma}}$ similarly to $\catname{EHyp_{\Sigma}}$.
    Recall the diagram below.
    \[
    \adjustbox{scale=1}{
        \begin{tikzcd}
        Z \arrow[r, "f"] \arrow[d, "g"']                                   & X \arrow[d, "\sfrac{i_1}{\sim R}"] \arrow[rdd, "j_1", bend left] &   \\
        Y \arrow[r, "\sfrac{i_2}{\sim R}"] \arrow[rrd, "j_2"', bend right] & \sfrac{X+Y}{\sim R} \arrow[rd, "u"]                              &   \\
                                                                        &                                                                  & Q
        \end{tikzcd}
    }
    \]

    The pushout of e-hypergraphs $X$ and $Y$ is computed in two steps.
    First, a coproduct of $X+Y$ is computed which is 
    \[
        X + Y = \{V_{X} + V_{Y}, E_{X} + E_{Y}, s_{X+Y}, t_{X+Y}, \#_{X+Y}, <_{c,X+Y} \}
    \]

@@

    % \update{Now $<_{c,{X+Y}} : V_{X} + V_{Y} + E_{X} + E_{Y} \to E_{X} + E_{Y} + \bot_{X} + \bot_{Y}$
    % And let's get back to the case when $<_{c,Z}^{\mu}(z) = \bot_{Z}$, $<_{c,X}^{\mu}(f_{V}(z)) = \bot_{X}$, $f_{E}(\bot_{Z}) = \bot_{X}$ and $g_{E}(\bot_{Z}) = <_{c,Y}^{\mu}(g_{V}(z))$
    % We then want to show that $[<_{c,X+Y}^{\mu}(f_{V};i_{1,V}(z))] = [<_{c,X+Y}^{\mu}(g_{V};i_{2,V}(z))]$
    % Note that we have $[i_{1,E}(\bot_{X})] = [i_{2,E}(<_{c,Y}^{\mu}(g_{V}(z)))]$ and $[<_{c,X+Y}^{\mu}(f_{V};i_{1,V}(z))] = [i_{1,V}(\bot_{X})]$ because $i_{1,V}$ is a coproduct injection and $<_{c}^{\mu}(\bot) = \bot$.
    % Now, because $g_{V};i_{2,V}$ is a homomorphism: $<_{c,X+Y}^{\mu}(g_{V};i_{2,V}(z)) = g_{V};i_{2,V}(<_{c,Z}(z)) = i_{2,V}(<_{c,Y}^{\mu}(g_{V}(z)))$
    % }
    We then quotient the sets of edges and nodes in $X + Y$ by $R_{V},R_{E}$
    \[
        \sfrac{X + Y}{\sim (R_{V},R_{E})} = \{\sfrac{V_{X} + V_{Y}}{\sim R_{V}}, \sfrac{E_{X} + E_{Y}}{\sim R_{E}}, \sfrac{s_{X+Y}}{\sim (R_{V},R_{E})}, \sfrac{t_{X,Y}}{\sim (R_{V},R_{E})}, \#_{\sfrac{X+Y}{\sim (R_{V},R_{E})}}, <_{c,\sfrac{X + Y}{\sim (R_{V},R_{E})}} \}    
    \]
    where quotienting on source and target functions is taken as in $Hyp_{\Sigma}$ and we will further omit writing the relations explicitly.
    Recall that $<_{c}$ is essentially a transitive clousure of $<_{c}^{\mu}$ and hence we can first define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]_{E})$ and $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]_{V})$.
    For this we will consider several cases where \update{$f$ and $g$ are mono. I require mono just to simplify things, we can get rid of this requirement if everything else is ok.}.
    Assume that $u$ is an element of $E_{X+Y}$ (the case for a node is similar).
    \begin{enumerate}
        \item $u$ has a pre-image $z$ in $E_{Z}$, $[z) \not = \varnothing$.
              The last requirement means that there necessarily exist $x = <_{c,X}^{\mu}(f_{E}(z)) = f_{E}(<_{c,Z}^{\mu}(z))$ and $y = <_{c,Y}^{\mu}(g_{E}(z)) = g_{E}(<_{c,Z}^{\mu}(z))$.
              We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [<_{c,X+Y}^{\mu}(u)]$
        \item $u$ has a pre-image $z$ in $E_{Z}$, $[z) = \varnothing$ and $[f(z)) = \varnothing$ $[g(z)) \not = \varnothing$.
              The last condition means that there exists $e_y = <_{c,Y}^{\mu}(g(z))$.
              We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [g_{E};<_{c,Y}^{\mu};i_{2,E}(z)] = [i_{2,E}(e_y)]$.
        \item $u$ has a pre-image $z$ in $E_{Z}$, $[z) = \varnothing$ and $[f(z)) \not = \varnothing$ $[g(z)) = \varnothing$.
              The one before the last condition means that there exists $e_x = <_{c,X}^{\mu}(f(z))$.
              We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [f_{E};<_{c,X}^{\mu};i_{1,E}(z)] = [i_{1,E}(e_x)]$.
        \item $u$ has no pre-image in $Z$ and then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [<_{c,X+Y}^{\mu}(u)]$
    \end{enumerate}
    Clearly, all the cases above are disjoint.
    Let's check that this is a well-defined function.
    Suppose $t_1 \sim t_2$ then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_1]) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_2])$.
    $t_1 \sim t_2$ implies there is $z$ such that $t_1 = f_{E};i_{1,E}(z)$ and $t_2 = g_{E};i_{2,E}(z)$.
    Then we need to consider the first three cases outlined above.
    \begin{itemize}
        \item If there exists $z' = <_{c,Z}^{\mu}(z)$ then 
        \[
            [<_{c,X+Y}^{\mu}(f_{E};i_{1,E}(z))] = [f_{E};i_{1,E}(<_{c,Z}^{\mu}(z))] = [f_{E};i_{1,E}(z')]
        \]
        \[
            [<_{c,X+Y}^{\mu}(g_{E};i_{2,E}(z))] = [g_{E};i_{2,E}(<_{c,Z}^{\mu}(z))] = [g_{E};i_{2,E}(z')]
        \]
        and
        \[ 
            [f_{E};i_{1,E}(z')] = [g_{E};i_{2,E}(z')]
        \]
        by commutativity.
        \item The other conditions satisfy functionality by definition.
    \end{itemize}

>>>>

    An e-hypergraph $\mathcal{G}$ over a monoidal signature $\Sigma$ is a tuple \[(V_{\mathcal{G}},E_{\mathcal{G}},s,t,l,<_c,\#)\] where $(V_{\mathcal{G}},E_{\mathcal{G}},s,t)$ are the same as in~\ref{def:hypergraph}.
    The labelling $l$ is modified to include an extra value $\bot \;$ $l :E_{\mathcal{G}} \to \Sigma + 1$. 
    % With an abuse of notation, we will confuse $\mathcal{G}$ with $V_{\mathcal{G}} \cup E_{\mathcal{G}}$, when treating it as a set.
    \question{Shall I use $\cup$ instead of $+$?}
    $<_c \subset (V_\mathcal{G} + E_\mathcal{G}) \times (V_\mathcal{G} + E_\mathcal{G})$ is a child relation imposing a strict partial order on $(V_\mathcal{G} + E_\mathcal{G})$.
    We require that for a given $x \in (V_\mathcal{G} + E_\mathcal{G})$ a set of all predecessors of $x\;$ $[x) = \{x' \in E_\mathcal{G} \;||\; x' <_c x\; \}$ is finite and consists of edges $e \in E_{\mathcal{G}}$ such that $l(e) = \bot$ only.
    Next, each $x$ has at most one immediate predecessor.
    \update{We will denote the fact that $e$ is an immediate predecessor of $v$ as $e <_c^{\mu} v$.}
    % , which essentially makes $<_{c}$ into a function that for any given $x$ returns its immediate predecessor.
    Such order was called a \textbf{well-founded arborescent} strict partial order in~\cite{orders_and_events}.
    Similarly, a set of all successors is $(x] = \{x' \in (V_\mathcal{G} + E_\mathcal{G}) \; ||\; x <_{c} x'\}$ where $x'$ can be a node or an edge. 
    % An edge $e \in E_{\mathcal{G}}$ is unlabelled, i.e. $l(e) = \bot$ iff $(e] \not = \varnothing$.
    Finally, we require that $<_c^{\mu}$ respects connectivity, i.e. if $v \in s(e)$ then $e' <_c^{\mu} e$ iff $e' <_c^{\mu} v$.

    $\langle (V_\mathcal{G} + E_\mathcal{G}), <_c, \# \rangle$ is an event-structure where $\# \subset (V_\mathcal{G} + E_\mathcal{G}) \times (V_\mathcal{G} + E_\mathcal{G})$ is an irreflexive symmetric relation called \textit{conflict} relation which satisfies the following
    \begin{enumerate}
        \label{def:e-hypergraph-req}
        \item 
        \[
    \forall x_1, x_2, x_3 \in (V_\mathcal{G} + E_\mathcal{G}) \text{, if } x_1 <_c x_2 \text{ and } x_1 \# x_3 \text{ then } x_2 \# x_3
    \] 
    if $x_1 <_c x_2$ we say that conflict $x_2 \# x_3$ is inherited from the conflict $x_1 \# x_3$. If the conflict is not inherited we say it is \textit{immediate} and denote it with $\#_{\mu}$
    \item $<_c$ and $\#$ are mutually exclusive
    \item $\#$ is defined \textit{only} for $x \in (V_\mathcal{G} + E_\mathcal{G})$ such that $[x) \not \eq \varnothing$
    \item $\#$ should respect connectivity
    \item \update{Complement of $\conflict_{\mu}$ should be transitive}
    \item for all distinct $x_1, x_2, x_3 \in (V_\mathcal{G} + E_\mathcal{G})$ $x_1 \#_{\mu} x_2$ and $x_2 \#_{\mu} x_3$ implies $x_1 \#_{\mu} x_3$
    \item for all $x, x' \in (V_\mathcal{G} + E_\mathcal{G})$ $x \#_{\mu} x'$ implies $[x) = [x')$
        \end{enumerate}

@@

    % \item
    % $x_1 \#_{\mathcal{F}} x_2$ iff $\phi(x_1) \#_{\mathcal{G}} \phi(x_2)$, where $x_1, x_2 \in \mathcal{F}$

        \item
    if $x_1 \#_{\mathcal{F}} x_2$ then $\phi(x_1) \#_{\mathcal{G}} \phi(x_2)$, where $x_1, x_2 \in \mathcal{F}$.
    Or, written functionally, when $x \in E_{\mathcal{F}}$
    \[
        \langle \phi_{V};i_{V_{\mathcal{G}}}, \phi_{E};i_{E_{\mathcal{G}}} \rangle^{*}(\conflict_{\mathcal{F}}(i_{E_{\mathcal{F}}}(x)))
        \subseteq
        \conflict_{\mathcal{G}}(\phi_{E};i_{E_{\mathcal{G}}}(x))
    \]
    , where $\phi_{V};i_{V_{\mathcal{G}}} : V_{\mathcal{F}} \to V_{\mathcal{G}} + E_{\mathcal{G}}$, and similarly for $\phi_{E};i_{E_\mathcal{G}}$ so that $\langle \phi_{V};i_{V_{\mathcal{G}}}, \phi_{E};i_{E_{\mathcal{G}}} \rangle : V_{\mathcal{F}} + E_{\mathcal{F}} \to  V_{\mathcal{G}} + E_{\mathcal{G}}$.
    And, when $x \in V_{\mathcal{F}}$
    \[
        \langle \phi_{V};i_{V_{\mathcal{G}}}, \phi_{E};i_{E_{\mathcal{G}}} \rangle^{*}(\conflict_{\mathcal{F}}(i_{V_{\mathcal{F}}}(x)))
        \subseteq
        \conflict_{\mathcal{G}}(\phi_{V};i_{V_{\mathcal{G}}}(x))
    \]
    Or, on per-component basis, if $i_{E_{\mathcal{F}}}(x_1) \in \conflict_{\mathcal{F}}(i_{E_{\mathcal{F}}}(x_2))$ then $i_{E_{\mathcal{G}}}(\phi_{E}(x_1)) \in \conflict_{\mathcal{G}}(i_{E_{\mathcal{G}}}(\phi_{E}(x_2)))$ and similarly for other types of $x_1,x_2$.
\end{enumerate}

% \update{Let's denote the fact of $x_1$ being the immediate predecessor of $x_2$ by $x_1 <_{\mu} x_2$.
%  Also, note that preserving the immediate predecessor implies preserving order.
% Homomorphism definition seems to be fine: by not requiring the \textit{only if} direction in bullet 2 we basically allow either of two things

% \begin{itemize}
%     \item $\phi(x_1) <_{\mu} \phi(x_2)$ and $x_1 <_{\mu} x_2$
%     \item $\phi(x_1) <_{\mu} \phi(x_2)$ and $x_1$ is unrelated to $x_2$
% \end{itemize}

% We can not have $\phi(x_1) <_{\mu} \phi(x_2)$ and $x_1 < x_2$, i.e. the case where $x_1$ is not the immediate predecessor of $x_2$ because then it would mean that there exists at least $x_3$ such that $x_1 <_{\mu} x_3 <_{\mu} x_2$ and because $\phi$ should preserve them it would mean that $\phi(x_1) <_{\mu} \phi(x_3) <_{\mu} \phi(x_2)$ implying that $\phi(x_2)$ has two immediate predecessors: $\phi(x_1)$ and $\phi(x_3)$.
% Of course, if $\phi$ does not identify $x_1$ and $x_3$.
% The first bullet is fine because it means that $\phi$ reflects the immediate predecessor.
% The second bullet leaves us with two options depicted above.

% \begin{figure}
%     \centering
% \begin{subfigure}{0.4\linewidth}

% \scalebox{0.5}{
% \begin{tikzpicture}
% 	\begin{pgfonlayer}{nodelayer}
% 		\node [style=node, label={above:$x_1$}] (19) at (-3.5, -4.5) {};
% 		\node [style=node, label={above:$x_2$}] (20) at (-4.5, -6.5) {};
% 		\node [style=node, label={above:$x_3$}] (21) at (-2.5, -6.5) {};
% 		\node [style=node, label={above:$x_4$}] (22) at (-3.5, -8.5) {};
% 		\node [style=node, label={above:$x_5$}] (23) at (-1.5, -8.5) {};
% 		\node [style=node, label={right:$x_2$}] (24) at (4.5, -5.5) {};
% 		\node [style=node, label={above:$x_1$}] (25) at (4.5, -2.5) {};
% 		\node [style=node, label={below:$x_5$}] (26) at (4.5, -11.5) {};
% 		\node [style=none] (27) at (4.5, -7.5) {};
% 		\node [style=none] (28) at (4.5, -9.5) {};
% 		\node [style=none] (29) at (4.5, -8.5) {$\vdots$};
% 		\node [style=none] (30) at (0.5, -6.5) {};
% 		\node [style=none] (31) at (2.5, -6.5) {};
% 		\node [style=none] (32) at (1.5, -5.5) {$\phi$};
% 	\end{pgfonlayer}
% 	\begin{pgfonlayer}{edgelayer}
% 		\draw (19) to (20);
% 		\draw (19) to (21);
% 		\draw (21) to (22);
% 		\draw (21) to (23);
% 		\draw (24) to (27.center);
% 		\draw (26) to (28.center);
% 		\draw (25) to (24);
% 		\draw [style=diredge] (30.center) to (31.center);
% 	\end{pgfonlayer}
% \end{tikzpicture}

% \caption{Case 1}
% \end{subfigure}
% \hfill
% \begin{subfigure}{0.4\linewidth}

% \scalebox{0.5}{
% \begin{tikzpicture}
% 	\begin{pgfonlayer}{nodelayer}
% 		\node [style=node, label={above:$x_1$}] (19) at (-6.5, -4.5) {};
% 		\node [style=node, label={above:$x_2$}] (20) at (-7.5, -6.5) {};
% 		\node [style=node, label={above:$x_3$}] (21) at (-5.5, -6.5) {};
% 		\node [style=node, label={above:$x_4$}] (30) at (-3, -4.5) {};
% 		\node [style=node, label={above:$x_1$}] (31) at (2.5, -4.5) {};
% 		\node [style=node, label={above:$x_2$}] (32) at (1.5, -6.5) {};
% 		\node [style=node, label={above:$x_3$}] (33) at (2.75, -6.5) {};
% 		\node [style=node, label={above:$x_4$}] (34) at (4, -6.5) {};
% 		\node [style=none] (35) at (-1.5, -5.5) {};
% 		\node [style=none] (36) at (-0.5, -5.5) {};
% 		\node [style=none] (37) at (-1, -5) {$\phi$};
% 	\end{pgfonlayer}
% 	\begin{pgfonlayer}{edgelayer}
% 		\draw (19) to (20);
% 		\draw (19) to (21);
% 		\draw (31) to (32);
% 		\draw (31) to (33);
% 		\draw (31) to (34);
% 		\draw [style=diredge] (35.center) to (36.center);
% 	\end{pgfonlayer}
% \end{tikzpicture}

% \caption{Case 2}

% \end{subfigure}
% \end{figure}

% \update{Case (a) above is impossible on two occasions: for the image of $x_5$ to be a successor of the image of $x_2$, $x_5$ itself should be hierarchical. Then, because $\phi$ should preserve the immediate predecessor, the image of $x_3$ should be the immediate predecessor of the image of $x_5$ and the image of $x_1$ should be the immediate predecessor of the image of $x_3$ and of the image of $x_2$. Since the image of $x_2$ is a successor of the image of $x_5$ on the right there should be two paths from the image of $x_5$ to the image of $x_1$ one through the image of $x_3$ and another through the image of $x_2$, this effectively means that some node on this path has two immediate predecessors.

% The case (b) above typechecks (for typed e-hypergraphs) only if $x_4$ is of type $0 \to 0$. This case is fine because we always can append, e.g. an edge, to a hierarchical edge using the semilattice equations (the one for tensoring the box). This also assumes that the image is down-closed.
% }

% \question{There is an issue with requiring that $\phi$ should reflect the conflict though. When we consider e-cospans and the maps from the interfaces to the carrier we map some nodes from the interface to conflicted nodes in the carrier. However, these nodes in the interface can not be in conflict as they have no predecessors. We can ask that this is a property of a matching morphism $m$ rather than arbitrary homomorphism. The same was done for down-closed-ness, for example.
% }

@@

    We will compute pushouts in $\catname{EHyp_{\Sigma}}$ similarly to $\catname{Hyp_{\Sigma}}$ but additionally will make a few assumptions.
    Recall the diagram below.
    \[
    \adjustbox{scale=1}{
        \begin{tikzcd}
        Z \arrow[r, "f"] \arrow[d, "g"']                                   & X \arrow[d, "\sfrac{i_1}{\sim R}"] \arrow[rdd, "j_1", bend left] &   \\
        Y \arrow[r, "\sfrac{i_2}{\sim R}"] \arrow[rrd, "j_2"', bend right] & \sfrac{X+Y}{\sim R} \arrow[rd, "u"]                              &   \\
                                                                        &                                                                  & Q
        \end{tikzcd}
    }
    \]

    First, we assume that $Z$ is a \textit{discrete} e-hypergraph, i.e. it has no edges.

    Then, the pushout of e-hypergraphs $X$ and $Y$ is computed in two steps.
    First, a coproduct of $X+Y$ is computed which is 
    \[
        X + Y = \{V_{X} + V_{Y}, E_{X} + E_{Y}, s_{X+Y}, t_{X+Y}, \#_{X+Y}, <_{c,X+Y} \}
    \]

@@

    % \update{Now $<_{c,{X+Y}} : V_{X} + V_{Y} + E_{X} + E_{Y} \to E_{X} + E_{Y} + \bot_{X} + \bot_{Y}$
    % And let's get back to the case when $<_{c,Z}^{\mu}(z) = \bot_{Z}$, $<_{c,X}^{\mu}(f_{V}(z)) = \bot_{X}$, $f_{E}(\bot_{Z}) = \bot_{X}$ and $g_{E}(\bot_{Z}) = <_{c,Y}^{\mu}(g_{V}(z))$
    % We then want to show that $[<_{c,X+Y}^{\mu}(f_{V};i_{1,V}(z))] = [<_{c,X+Y}^{\mu}(g_{V};i_{2,V}(z))]$
    % Note that we have $[i_{1,E}(\bot_{X})] = [i_{2,E}(<_{c,Y}^{\mu}(g_{V}(z)))]$ and $[<_{c,X+Y}^{\mu}(f_{V};i_{1,V}(z))] = [i_{1,V}(\bot_{X})]$ because $i_{1,V}$ is a coproduct injection and $<_{c}^{\mu}(\bot) = \bot$.
    % Now, because $g_{V};i_{2,V}$ is a homomorphism: $<_{c,X+Y}^{\mu}(g_{V};i_{2,V}(z)) = g_{V};i_{2,V}(<_{c,Z}(z)) = i_{2,V}(<_{c,Y}^{\mu}(g_{V}(z)))$
    We then quotient the sets of edges and nodes in $X + Y$ by $R_{V},R_{E}$
        \sfrac{X + Y}{\sim (R_{V},R_{E})} = \{\sfrac{V_{X} + V_{Y}}{\sim R_{V}}, \sfrac{E_{X} + E_{Y}}{\sim R_{E}}, \sfrac{s_{X+Y}}{\sim (R_{V},R_{E})}, \sfrac{t_{X,Y}}{\sim (R_{V},R_{E})}, \#_{\sfrac{X+Y}{\sim (R_{V},R_{E})}}, <_{c,\sfrac{X + Y}{\sim (R_{V},R_{E})}} \}    
    where quotienting on source and target functions is taken as in $Hyp_{\Sigma}$ and we will further omit writing the relations explicitly.
    Recall that $<_{c}$ is essentially a transitive clousure of $<_{c}^{\mu}$ and hence we can first define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]_{E})$ and $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]_{V})$.
    For this we will consider several cases where \update{$f$ and $g$ are mono. I require mono just to simplify things, we can get rid of this requirement if everything else is ok.}.
    Assume that $u$ is an element of $V_{X+Y}$.
        % \item $u$ has a pre-image $z$ in $V_{Z}$, $[z) \not = \varnothing$.
        %       The last requirement means that there necessarily exist $x = <_{c,X}^{\mu}(f_{E}(z)) = f_{E}(<_{c,Z}^{\mu}(z))$ and $y = <_{c,Y}^{\mu}(g_{E}(z)) = g_{E}(<_{c,Z}^{\mu}(z))$.
        %       We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [<_{c,X+Y}^{\mu}(u)]$
        \item $u$ has a pre-image $z$ in $V_{Z}$ (by discreteness, $[z) = \varnothing$) and $[f_{V}(z)) = \varnothing$ $[g_{V}(z)) \not = \varnothing$.
              The last condition means that there exists $e_y = <_{c,Y}^{\mu}(g_{V}(z))$.
              We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [g_{V};<_{c,Y}^{\mu};i_{2,E}(z)] = [i_{2,E}(e_y)]$.
        \item $u$ has a pre-image $z$ in $V_{Z}$, (by discreteness, $[z) = \varnothing$) and $[f_{V}(z)) \not = \varnothing$ $[g_{V}(z)) = \varnothing$.
              The one before the last condition means that there exists $e_x = <_{c,X}^{\mu}(f_{V}(z))$.
              We then define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [f_{V};<_{c,X}^{\mu};i_{1,E}(z)] = [i_{1,E}(e_x)]$.
        \item $u$ has no pre-image in $Z$ and then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [<_{c,X+Y}^{\mu}(u)]$
    \question{In the case when images of $f$ and $g$ are top-level the function is undefined. Shall we introduce bottom?}
    Now, if $u$ is an element of $E_{X+Y}$.
        \item We have the only case of $u$ having no pre-image in $E_{Z}$ because its empty.
              Hence, we define $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([u]) = [<_{c,X+Y}^{\mu}(u)]$.
    \question{I decided to keep Z discrete, otherwise the number of cases to consider within the proofs is too large.
    This also means that we now can identify only nodes.
    I will make changes to account for this later.
    \update{If $f$ and $g$ are not mono, the definitions stay the same as $i_{2,E}$ and $i_{1,E}$ are mono.}
    Clearly, all the cases above are disjoint.
    Let's check that this is a well-defined function.
    Suppose $t_1, t_2$ are nodes and $t_1 \sim t_2$, then $<_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_1]) = <_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_2])$.
    $t_1 \sim t_2$ implies there is $z$ such that $t_1 = f_{V};i_{1,V}(z)$ and $t_2 = g_{V};i_{2,V}(z)$ and either $[f_{V}(t_1)) = \varnothing$ or $[g_{V}(z)) = \varnothing$.
    Assume the latter, then, by definition.
        <_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_1]) = [f_{V};<_{c,X}^{\mu};i_{1,E}(z)]    
        <_{c,\sfrac{X+Y}{\sim}}^{\mu}([t_2]) = [f_{V};<_{c,X}^{\mu};i_{1,E}(z)]    
    so we have well-defined-ness on the nose.
